An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-10 VLDB2026/main.tex
Update main.tex
change the filter type of ACORN

\setlength{\textfloatsep}{0cm}
\setlength{\floatsep}{0cm}
\begin{table*}[t]
	\centering
        %\setlength{\belowcaptionskip}{-0.3cm}
      \setlength{\abovecaptionskip}{0.1cm}
     \setlength{\belowcaptionskip}{-0.2cm}
	\caption{Comparison of AF-ANN search algorithms}
	\small
	\label{tab:compair_1}
    \begin{tabular}{|l|l|c|c|c|c|c|c|c|}
		\hline
        \textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		\hline
         NHQ & Graph & C & Y & N& N& N & N & N \\
         FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
	StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
        CAPS & IVF & C & Y & N & N & N & Y & Y \\
        ACORN & Graph & C & Y & Y & Y & Y & Y & Y \\
       UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
        Puck & IVF & B & Y & Y & Y & N & Y & Y \\
        % ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\

>>>>

\setlength{\textfloatsep}{0cm}
\setlength{\floatsep}{0cm}
\begin{table*}[t]
	\centering
        %\setlength{\belowcaptionskip}{-0.3cm}
      \setlength{\abovecaptionskip}{0.1cm}
     \setlength{\belowcaptionskip}{-0.2cm}
	\caption{Comparison of AF-ANN search algorithms}
	\small
	\label{tab:compair_1}
    \begin{tabular}{|l|l|c|c|c|c|c|c|c|}
		\hline
        \textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		\hline
         NHQ & Graph & C & Y & N& N& N & N & N \\
         FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
	StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
        CAPS & IVF & C & Y & N & N & N & Y & Y \\
        ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
       UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
        Puck & IVF & B & Y & Y & Y & N & Y & Y \\
        % ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
